Working memory performance in adverse environments: Enhanced, impaired, or intact?

### 2024-01-22 README.Rmd
update README files

>>>>

```{r results ='asis', echo = FALSE}
gert::git_tag_list() |> 
  mutate(
    tags = pmap(list(name = name, ref = ref, commit = commit), function(name, ref, commit) {
      gert::git_commit_info(commit) |> 
        as_tibble() |> 
        select(commit = id, author, time, message) 
    })
  ) |> 
  select(-commit, -ref) |> 
  unnest(tags) |> 
  separate(message, into = c("description", "hash", "code"), sep = "\\n") |> 
  mutate(
    name = map_chr(name, function(name) {
      name |> 
        str_remove("\\[\\[") |>
        str_remove("\\d*$") |> 
        str_replace("_", " ") |> 
        str_to_title()
    })
  ) |> 
  mutate(
    code = str_remove_all(code, "^code\\s") |> str_replace_all(string = _, "\\|\\>", "\\|\\>\\\n"),
    link_to_git = paste0(
       gert::git_remote_list()$url |> str_remove(string = _, pattern = "\\.git$"), "/tree/", commit)
    ) |>
  arrange(desc(time)) |> 
  glue_data("  - **[{time}]({link_to_git}): {description}**
        - **Milestone:** {name}
        - **Data MD5 hash**: {hash}
        - [Link to code snippet](https://https://github.com/StefanVermeent/abcd_ddm/tree/main/.projectlog/{commit}.R)
        \n
    ")
```
